\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-24 eg6-letters/NIM/EG6_RTPC_NIM.tex
added the performance section

\section{Track Reconstruction}\label{sec_perf}

In order to reconstruct tracks we first select good hits. This means rejecting 
out-of-time hits and hits linked to the electronic noise. The second step is 
to reconstruct the spacial origin of the hits using the extracted drift speed and drift path 
parameters. For each registered hit, we calculate a position of emission from 
the recorded time and the position of the recording pad. The third step 
is to create chains of hits. The maximum distance between two close adjacent 
hits has to be less than 10.5 mm to chain them, this roughly correspond to 
neighbors and next to neighbors. Then, we fit the chains that have a minimum of 
10 hits. We make the fit in two iterations, first, all the hits of the chain 
together with the beam line are fitted with a helix. For the second iteration, 
the hits that are 5 mm or farther from the first fit are excluded.

@@

{\bf \color{red} Mohammad: We need some performance studies here, I remember we had
figures showing efficiency, we need to add them.}

>>>>

\section{Track Reconstruction}\label{sec_rec}
In order to reconstruct tracks we first select good hits. This means rejecting 
out-of-time hits and hits linked to the electronic noise. The second step is 
to reconstruct the spacial origin of the hits using the extracted drift speed and drift path 
parameters. For each registered hit, we calculate a position of emission from 
the recorded time and the position of the recording pad. The third step 
is to create chains of hits. The maximum distance between two close adjacent 
hits has to be less than 10.5 mm to chain them, this roughly correspond to 
neighbors and next to neighbors. Then, we fit the chains that have a minimum of 
10 hits. We make the fit in two iterations, first, all the hits of the chain 
together with the beam line are fitted with a helix. For the second iteration, 
the hits that are 5 mm or farther from the first fit are excluded.

@@

\section{Performance Studies}\label{sec_perfor}
The previous discussions have shown that the two modules of the RTPC have 
slightly different yield, however this yield should not be linked to a 
different performance of the RTPC. The differences are mainly due to 
complicated convolution of CLAS and the RTPC acceptances. We measured the 
efficiency of the RTPC using the elastic scattering on $^4$He, where the 
exclusive elastic yield is compared to the inclusive yield for the two modules 
of the detector. Here the inclusive yields are the number of electrons in the 
elastic invariant mass peak whose corresponding elastically scattered $^4$He 
would have been in the acceptance of the RTPC, and the exclusive yields require 
the additional detection of the $^4$He. As a result, we found that the left and 
the right modules have similar efficiencies except near the target windows, as 
shown in figure \ref{fig:rtpc_eff}.

\begin{figure}[tb]
\centering
\includegraphics[width=8cm]{fig/tpceff.png}
\caption{The RTPC $^4$He detection efficiency as a function of the longitudinal 
   position along the detector.
 \label{fig:rtpc_eff}}
 \end{figure}
